pdfimager
=========

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![R-check](https://github.com/sckott/pdfimager/workflows/R-check/badge.svg)](https://github.com/sckott/pdfimager/actions/)


`pdfimager` - Extract images from pdfs

Docs: <https://sckott.github.io/pdfimager/>

This packages uses `sys` R package to "shell out" to pdfimages. Apparently pdfimages is not in poppler cpp, so is not in pdftools R pkg

## Install pdfimages

pdfimages is installed when you install poppler

Installation instructions can be found at <https://poppler.freedesktop.org/>

## Install pdfimager

```{r eval=FALSE}
remotes::install_github("sckott/pdfimager")
```

```{r}
library("pdfimager")
```

## help info

```{r}
pdimg_help()
```

## pdf image metadata

```{r}
x <- system.file("examples/BachmanEtal2020.pdf", package="pdfimager")
pdimg_meta(x)
```

## pdf images

```{r}
x <- system.file("examples/BachmanEtal2020.pdf", package="pdfimager")
pdimg_images(x)
```

## filter images

does a variety of thing to filter images by their metadata, some are configureable

```{r}
x1 <- system.file("examples/Tierney2017JOSS.pdf", package="pdfimager")
x2 <- system.file("examples/vanGemert2018.pdf", package="pdfimager")
res <- pdimg_images(c(x1, x2))
vapply(res, NROW, 1)
out <- pdimg_filter(res)
vapply(out, NROW, 1)
```

## Meta

* Please [report any issues or bugs](https://github.com/sckott/pdfimager/issues)
* License: MIT
* Please note that the pdfimager project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
